Influence of journal data archiving mandates on author attitudes, experiences,

### 2018-05-02 manuscript.Rmd
add two more refs

---
title: Influence of journal data archiving mandates on author attitudes, experiences,
  and practices
author: "Heather A. Piwowar, Todd J. Vision"
csl: peerj.csl
output:
  md_document:
    variant: markdown_github
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

@@

>>>>

---
title: Influence of journal data archiving mandates on author attitudes, experiences,
  and practices
author: "Heather A. Piwowar, Todd J. Vision"
csl: peerj.csl
output:
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

@@

Also work in these:
- The influence of journal submission guidelines on authors' reporting of statistics and use of open research practices: bib["giofre2017the-inf"]
- Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psycholog: bib["nuijten"]
